---
title: "Highlight code"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Highlight code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(highlighter)
```

## Using highlighter
We can use the `highglighter` function in order to render and highlight code.
By default the function will highlight the syntax of R code.

```{r}
highlighter("some_variable <- 3")
```

If we want we can specify the language using the `language` parameter.

```{r}
highlighter("const someVariable = 3;", language = "js")
```

## Using highlight_file
We can pass the path to a local file using the `highlight_file` function

```{r eval = FALSE}
# Specifying the language to be used
highlight_file("<path_to_your_file>", language = "r")

# Auto guessing the language to be highlighted when the language
# parameter is not specified.
highlight_file("<path_to_your_file>")
```

## Using themes

Specifying a theme to be used. You can get the available themes by
means of the following function: `get_available_themes()`

```{r eval = FALSE}
# Specifying the language to be used and the theme
highlight_file("<path_to_your_file>", language = "r", theme = "dark")
```
